
```{r, include = FALSE}
ottrpal::set_knitr_image_path()
```

# cellxgene

## Learning Objectives
- Confirm access to STAC Administrators Group
- Launch cellxgene
- Edit SciServer Dashboard

## Instructions

### Confirm Access

1. Go to [sciserver.org](https://sciserver.org) and click on "**Login to SciServer**".

```{r, fig.alt="Image of SciServer landing page", out.width = "100%", echo = FALSE}
ottrpal::include_slide("https://docs.google.com/presentation/d/16jh1ov1PyRyPKMTJ7ROiEyNm1B5KxdQlYQovVBCYesk/edit#slide=id.g25a5f9f2e31_0_6")
```

2. Log in with the SciServer account you created in Part 1.

```{r, fig.alt="Image of SciServer login page", out.width = "100%", echo = FALSE}
ottrpal::include_slide("https://docs.google.com/presentation/d/16jh1ov1PyRyPKMTJ7ROiEyNm1B5KxdQlYQovVBCYesk/edit#slide=id.g25a5f9f2e31_0_11")
```

3. Once logged in, you will see options on the top menu bar of the homepage/Dashboard (Home, Files, Groups, and various options for Compute). Confirm that you received and accepted the invitation to the STAC Administrators Group by clicking on “**Groups**” in the top menu bar.

```{r, fig.alt="Image of SciServer Dashboard", out.width = "100%", echo = FALSE}
ottrpal::include_slide("https://docs.google.com/presentation/d/16jh1ov1PyRyPKMTJ7ROiEyNm1B5KxdQlYQovVBCYesk/edit#slide=id.g25a5f9f2e31_0_18")
```

4. Click on “**STAC Administrators**” in the left sidebar menu. You should see your username in the Members list on the right sidebar. You should also have access to the Shared Data Volume “STAC” and Share Compute Image “single-cell-explorer”.     

```{r, fig.alt="Image of SciServer Groups page", out.width = "100%", echo = FALSE}
ottrpal::include_slide("https://docs.google.com/presentation/d/16jh1ov1PyRyPKMTJ7ROiEyNm1B5KxdQlYQovVBCYesk/edit#slide=id.g25a5f9f2e31_0_24")
```

### Join Genomics Domain

1. Return to the [SciServer Dashboard](https://apps.sciserver.org/dashboard/).
2. Click on "**Science Domains**" in the top menu bar.

```{r, fig.alt="Image of SciServer Dashboard", out.width = "100%", echo = FALSE}
ottrpal::include_slide("https://docs.google.com/presentation/d/16jh1ov1PyRyPKMTJ7ROiEyNm1B5KxdQlYQovVBCYesk/edit#slide=id.g25a5f9f2e31_0_33")
```

3. In the left sidebar menu titled "Science Domains", click on "**Genomics**".

```{r, fig.alt="Image of Science Domains page", out.width = "100%", echo = FALSE}
ottrpal::include_slide("https://docs.google.com/presentation/d/16jh1ov1PyRyPKMTJ7ROiEyNm1B5KxdQlYQovVBCYesk/edit#slide=id.g25a5f9f2e31_0_39")
```

4. Beneath the DNA logo image, click the "**Join**" button.

```{r, fig.alt="Image of Genomics page", out.width = "100%", echo = FALSE}
ottrpal::include_slide("https://docs.google.com/presentation/d/16jh1ov1PyRyPKMTJ7ROiEyNm1B5KxdQlYQovVBCYesk/edit#slide=id.g25954290abf_0_0")
```

### Launch cellxgene

1. In order to explore the available datasets, click on “**Files**” in the top menu bar.

```{r, fig.alt="Image of Files page", out.width = "100%", echo = FALSE}
ottrpal::include_slide("https://docs.google.com/presentation/d/16jh1ov1PyRyPKMTJ7ROiEyNm1B5KxdQlYQovVBCYesk/edit#slide=id.g25a5f9f2e31_0_45")
```

2. Click on “**Data Volumes**” in the left sidebar menu. 

```{r, fig.alt="Image of Data Volumes submenu", out.width = "100%", echo = FALSE}
ottrpal::include_slide("https://docs.google.com/presentation/d/16jh1ov1PyRyPKMTJ7ROiEyNm1B5KxdQlYQovVBCYesk/edit#slide=id.g25a5f9f2e31_0_51")
```

3. Scroll down the page to find the data volume “**STAC**”. Click on the name to access the dashboard.

```{r, fig.alt="Image of STAC Data Volume highlighted", out.width = "100%", echo = FALSE}
ottrpal::include_slide("https://docs.google.com/presentation/d/16jh1ov1PyRyPKMTJ7ROiEyNm1B5KxdQlYQovVBCYesk/edit#slide=id.g25a5f9f2e31_0_57")
```

4. Under the “Available datasets” heading, click on “**PDAC [cellxgene]**”.

```{r, fig.alt="Image of PDAC dataset highlighted", out.width = "100%", echo = FALSE}
ottrpal::include_slide("https://docs.google.com/presentation/d/16jh1ov1PyRyPKMTJ7ROiEyNm1B5KxdQlYQovVBCYesk/edit#slide=id.g25a5f9f2e31_0_63")
```

5. cellxgene should now launch with your dataset of interest ready to explore!

```{r, fig.alt="Image of cellxgene window", out.width = "100%", echo = FALSE}
ottrpal::include_slide("https://docs.google.com/presentation/d/16jh1ov1PyRyPKMTJ7ROiEyNm1B5KxdQlYQovVBCYesk/edit#slide=id.g25a5f9f2e31_0_69")
```


### Edit Dashboard

1. Click on "**Files**" in the top menu bar.

```{r, fig.alt="Image of Files highlighted in the menu bar", out.width = "100%", echo = FALSE}
ottrpal::include_slide("https://docs.google.com/presentation/d/16jh1ov1PyRyPKMTJ7ROiEyNm1B5KxdQlYQovVBCYesk/edit#slide=id.g25a5f9f2e31_0_75")
```

2. Click on “**Data Volumes**” in the left sidebar menu.

```{r, fig.alt="Image of Data Volumes highlighted", out.width = "100%", echo = FALSE}
ottrpal::include_slide("https://docs.google.com/presentation/d/16jh1ov1PyRyPKMTJ7ROiEyNm1B5KxdQlYQovVBCYesk/edit#slide=id.g25a5f9f2e31_0_51")
```

3. Scroll down the page to find the data volume “**STAC**”. Click on the name to access the dashboard.

```{r, fig.alt="Image of STAC data volume highlighted", out.width = "100%", echo = FALSE}
ottrpal::include_slide("https://docs.google.com/presentation/d/16jh1ov1PyRyPKMTJ7ROiEyNm1B5KxdQlYQovVBCYesk/edit#slide=id.g25a5f9f2e31_0_57")
```

4. Scroll to the bottom of the page and find the “README.md” file. Click on the three dots, then click “**View/Edit**”.

```{r, fig.alt="Image of View/Edit option highlighted", out.width = "100%", echo = FALSE}
ottrpal::include_slide("https://docs.google.com/presentation/d/16jh1ov1PyRyPKMTJ7ROiEyNm1B5KxdQlYQovVBCYesk/edit#slide=id.g25a5f9f2e31_0_81")
```

5. You should now be able to edit and improve the README file using standard Markdown syntax.

```{r, fig.alt="Image of README file editor", out.width = "100%", echo = FALSE}
ottrpal::include_slide("https://docs.google.com/presentation/d/16jh1ov1PyRyPKMTJ7ROiEyNm1B5KxdQlYQovVBCYesk/edit#slide=id.g25a5f9f2e31_0_87")
```

                                                                                       
```{r}
devtools::session_info()
```
